A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-12-02 bioc-workflow.Rnw
updates based on Claire's comments

As demonstrated in \cite{hyper} and illustrated in the PCA plot
(figure \ref{fig:plotmarkers}), the Golgi apparatus proteins (dark
brown) display a dynamic pattern, noting sets of Golgi marker proteins
that are distributed amongst other subcellular structures, an
observation supported by microscopy.  As such, we are going to reset
the annotation of Golgi markers to unknown using the
\texttt{fDataToUnknown} function. It is often used to replace empty
strings (\texttt{""}) or missing values in the markers definition to a
common definition of \textit{unknown} localisation.

@@

>>>>

As demonstrated in \cite{hyper} and illustrated in the PCA plot
(Figure \ref{fig:plotmarkers}), the Golgi apparatus proteins (dark
brown) display a dynamic pattern, noting sets of Golgi marker proteins
that are distributed amongst other subcellular structures, an
observation supported by microscopy.  As such, we are going to reset
the annotation of Golgi markers to unknown using the
\texttt{fDataToUnknown} function. It is often used to replace empty
strings (\texttt{""}) or missing values in the markers definition to a
common definition of \textit{unknown} localisation.

@@

In addition, the reproducibility can be assessed by performing
independent classification analyses on each replicate (see the section
on \textit{Supervised machine learning} below) and comparing the the
results. Even when the gradient conditions different (for unexpected
technical or voluntary reasons, to maximise resolution when combining
experiments \cite{Trotter:2010}), one expects agreement in the most
confident organelle assignments.
